The title

### 2024-10-15 05_Manuscript/manuscript.Rmd
added item text to factor loadings output

nrow(efaDF_noout)
nrow(cfaDF_noout)
```

@@

```{r}
number_items <- fa.parallel(efaDF, #data frame
                            fm="ml", #math
                            fa="fa") #only efa
sum(number_items$fa.values > 1)
sum(number_items$fa.values > .7)
```

@@

```{r}
EFA_fit <- fa(efaDF, #data
              nfactors = 2, #number of factors
              rotate = "oblimin", #rotation
              fm = "ml") #math

@@

efa_loadings_2 <- as.data.frame(unclass(EFA_fit_2$loadings)) %>% 
  mutate(keep = ifelse(
    ML1 >= .30, "yes", ifelse(
      ML2 >= .30, "yes", ifelse(
        ML1 >= .30 & ML2 >= .30, "no", "no"
      )
    )
  )) %>% 
  mutate(question = rownames(.))
```

```{r}
EFA_fit <- fa(efaDF, #data
              nfactors = 3, #number of factors
              rotate = "oblimin", #rotation
              fm = "ml") #math

@@

efa_loadings_2 <- as.data.frame(unclass(EFA_fit_2$loadings)) %>% 
  mutate(keep = ifelse(
    ML1 >= .30, "yes", ifelse(
      ML2 >= .30, "yes", ifelse(
        ML3 >= .30, "yes", "no"
        )
      )
    )
  ) %>% 
  mutate(question = rownames(.)) %>% 
  mutate(
    keep = ifelse(
          (ML1 >= .30 & ML2 >= .30) | 
            (ML1 >= .30 & ML3 >= .30) |
            (ML3 >= .30 & ML2 >= .30), "no", keep
          )
  )
```

@@

@@

>>>>

nrow(efaDF_noout)
nrow(cfaDF_noout)

write.csv(efaDF, "../03_Data/efaDF.csv", row.names = F)
write.csv(cfaDF, "../03_Data/cfaDF.csv", row.names = F)
```

@@

```{r}
#efaDF <- read.csv("../03_Data/efaDF.csv")

number_items <- fa.parallel(efaDF, #data frame
                            fm="ml", #math
                            fa="fa") #only efa
sum(number_items$fa.values > 1)
sum(number_items$fa.values > .7)
```

@@

```{r}
item_text <- read.csv("../03_Data/item_text.csv")

EFA_fit <- fa(efaDF, #data
              nfactors = 2, #number of factors
              rotate = "oblimin", #rotation
              fm = "ml") #math

@@

efa_loadings_2 <- as.data.frame(unclass(EFA_fit_2$loadings)) %>% 
  mutate(keep = ifelse(
    ML1 >= .30, "yes", ifelse(
      ML2 >= .30, "yes", ifelse(
        ML1 >= .30 & ML2 >= .30, "no", "no"
      )
    )
  )) %>% 
  mutate(question = rownames(.))

## Make a dataframe with loadings and item text
model1_loadings <- efa_loadings_2
model1_loadings$ItemNum <- row.names(model1_loadings)
model1_withtext <- merge(item_text, model1_loadings, by = 'ItemNum')

```{r}

EFA_fit <- fa(efaDF, #data
              nfactors = 3, #number of factors
              rotate = "oblimin", #rotation
              fm = "ml") #math

@@

efa_loadings_2 <- as.data.frame(unclass(EFA_fit_2$loadings)) %>% 
  mutate(keep = ifelse(
    ML1 >= .30, "yes", ifelse(
      ML2 >= .30, "yes", ifelse(
        ML3 >= .30, "yes", "no"
        )
      )
    )
  ) %>% 
  mutate(question = rownames(.)) %>% 
  mutate(
    keep = ifelse(
          (ML1 >= .30 & ML2 >= .30) | 
            (ML1 >= .30 & ML3 >= .30) |
            (ML3 >= .30 & ML2 >= .30), "no", keep
          )
  )

model2_loadings <- efa_loadings_2
model2_loadings$ItemNum <- row.names(model2_loadings)
model2_withtext <- merge(item_text, model2_loadings, by = 'ItemNum')
```

@@

model3_loadings <- efa_loadings_3
model3_loadings$ItemNum <- model3_loadings$question
model3_withtext <- merge(item_text, model3_loadings, by = 'ItemNum')

@@

**Model 1: Two-Factor**

These are all the items with loading \> 0.7

-   Factor One: Sense of Contribution

    -   Q2_16: I have taken part in activities or events which will
        impact the future.

    -   Q2_2: I have contributed to the world in a unique way.

    -   Q2_3: I have contributed to causes that will impact the future.

    -   Q5_9: I have contributed to things which will be meaningful.

    -   Q5_13: I will leave a lasting legacy.

    -   Q2_5: I am proud of my accomplishments.

    -   Q2_6: I am confident in the legacy I will leave when I die.

    -   Q4_1: Others would say I have impacted their lives.

<!-- -->

-   Factor Two: Spiritual Immortality

    -   Q4_19: I believe in an afterlife.

    -   Q2_17: My spirit or soul will live on after I physically die.

    -   Q2_12: I believe I will live on in the afterlife.

    -   Q5_2: Death is not the end.

    -   Q5_10: I believe in an immaterial soul or spirit.

    -   Q5_1: I am comforted by the thought of an afterlife.

    -   Q2_18: Death will not be the end of me.

**Model 2: Three-Factor**

-   Factor One:

    -   Q2_16: I have taken part in activities or events which will
        impact the future.

    -   Q2_3: I have contributed to causes that will impact the future.

    -   Q2_5: I am proud of my accomplishments.

    -   Q5_9: I have contributed to things which will be meaningful.

    -   Q4_1: Others would say I have impacted their lives.

    -   Q2_4: I feel I have taken part in something bigger than myself.

    -   Q2_2: I have contributed to the world in a unique way.

<!-- -->

-   Factor Two:

    -   Q

<!-- -->

-   Factor Three:

    -   Q

**Model 3: Five-Factor**
